Reasoning About a Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management\\ Technical Appendix Including Proofs and Details

### 2019-02-25 local-capability-machine/arxiv/local-capability-machine.tex
[TOPLAS] Add arxiv tech report files

\author{Lau Skorstengaard\\Aarhus University\\\texttt{lask@cs.au.dk}
        \and 
        Dominique Devriese\\imec-DistriNet, KU Leuven\\\texttt{dominique.devriese@cs.kuleuven.be}
        \and 
        Lars Birkedal\\Aarhus University\\\texttt{birkedal@cs.au.dk}}

>>>>

\author{Lau Skorstengaard\\Aarhus University\\\texttt{lau@cs.au.dk}
        \and 
        Dominique Devriese\\Vrije~Universiteit~Brussel\\\texttt{dominique.devriese@vub.be}
        \and 
        Lars Birkedal\\Aarhus University\\\texttt{birkedal@cs.au.dk}}
